Survival Analysis

### 2014-04-27 paper.Rnw
Add sample computation table

\begin{document}
\SweaveOpts{concordance=TRUE}
\maketitle
<<echo = FALSE>>=
library(ggplot2)
library(gridExtra)
ws <- read.csv('worksheet.csv', header = TRUE)
ws$id <- sprintf('%02d', 1:nrow(ws))
@

@@

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}
\maketitle
<<echo = FALSE>>=
library(ggplot2)
library(gridExtra)
library(survival)
library(xtable)
ws <- read.csv('worksheet.csv', header = TRUE)
ws$id <- sprintf('%02d', 1:nrow(ws))
@

@@

Below is the result of this algorithm on the sample.

<<ws-table, echo = FALSE, results = tex>>=
ws.fit <- survfit(Surv(duration, event) ~ 1, data = ws)

ws.table <- with(ws.fit, data.frame(
  n = n.risk,
  d = n.event,
  c = n.censor,
  f = n.event / n.risk,
  nf = 1 - (n.event / n.risk),
  s = surv))

colnames(ws.table) <-
  c("$n_i$", "$d_i$", "$c_i$", "$\\nicefrac{d}{n}$", "$\\frac{n-d}{n}$", "$\\hat S_i$")

print(xtable(ws.table),
  sanitize.text.function = function(x) {
    return(x)
  })
@
